Human tissue specific markers

### 2017-06-08 manuscript/manuscript.Rnw
switch to CairoPDF

<<load.libraries,echo=FALSE,results="hide",warning=FALSE,message=FALSE,error=FALSE,cache=FALSE>>=
opts_chunk$set(dev="cairo_pdf",out.width="0.5\\textwidth",out.height="0.7\\textheight",out.extra="keepaspectratio")
opts_chunk$set(cache=TRUE, autodep=TRUE)
options(device = function(file, width = 8, height = 7, ...) {
  cairo_pdf(tempfile(), width = width, height = height, ...)
})
options(scipen = -1, digits = 2)
library("data.table")
library("ggplot2")
library("reshape2")
library("proto")
library("xtable")
library("caret")
library("pROC")
library("grid")
library("scales")

>>>>

<<load.libraries,echo=FALSE,results="hide",warning=FALSE,message=FALSE,error=FALSE,cache=FALSE>>=
opts_chunk$set(dev="CairoPDF",out.width="0.5\\textwidth",out.height="0.7\\textheight",out.extra="keepaspectratio")
opts_chunk$set(cache=TRUE, autodep=TRUE)
options(device = function(file, width = 8, height = 7, ...) {
  CairoPDF(tempfile(), width = width, height = height, ...)
})
options(scipen = -1, digits = 2)
library("data.table")
library("ggplot2")
library("reshape2")
library("proto")
library("xtable")
library("caret")
library("pROC")
library("grid")
library("scales")
